%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Swechha Jha}
\address{Bangalore , Karnataka}
\contacts{(+91) 8951120297 \linebreak swechhajha12@gmail.com \linebreak https://www.linkedin.com/in/swechha-jha-a38456129/ \linebreak https://github.com/swekshajha12}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Experience}
		\begin{cvsubsection}{ Intern}{Learn It Girl }{OCT 2017 - Present}
			Django Depression App		
			\begin{itemize}
				\item Implementation of Pygame to develop a maze game in Python.
				\item Implementation of Django to create a web app  and then host that app on server.
				%\item Redesigned chat file format and implemented backwards compatibility for search.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Development Intern}{Nucarbn}{Jun 2017-SEP 2017}	
			\begin{itemize}
				\item Worked on developing the alpha version of their healthcare platform.
				\item Helped build the backend component and the AWS related work.
				\item Worked with the Devops team to find a suitable platform for deployment.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Machine Learning Intern}{Catalan Labs}{APR 2017 - JUN 2017}		
			\begin{itemize}
				\item Worked on a project to predict the value of Bitcoins using Bayesian Regression.
				\item Researched about the various techniques and worked with the team to develop the algorithm.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Campus Leader}{Lean In India}{SEP 2017 -PRESENT}		
			\begin{itemize}
				\item Responsible for creating a campus circle of students to enhance the feeling of mutual support and understanding . 
				\item The circle is also technically active and we discuss coding questions , recent technologies , and various tech topics (web dev , python , machine learning ).
			\end{itemize}
			\begin{cvsubsection}{Campus Executive}{Mozilla}{MAR 2017-PRESENT
			\begin{itemize}
				\item Held a workshop with other fellow executives on Open source and Git.
				\item Work with other students to create awareness about open source and encourage them to contribute.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{BE , CSE}{Sir. M.Visvesvaraya Institute of Technology}{AUG 2015-- JUL 2019}
			\begin{itemize}
				\item Computer Science Engineering | Current Aggregate 8.5/10
				\item Undergraduate Coursework:  Databases; Algorithms; Programming Languages; Comp. Architecture; Engineering Entrepreneurship,Artificial Intelligence.
			\end{itemize}
		\begin{cvsubsection}{Class 10th and 12th}{K.V.NO.2 Kanpur}
			\begin{itemsize}
				\item Class 10th result: 10 CGPA 
				\item Class 12th result: 91.6%
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Accident Preventor} .A project to prevent accidents on hairpin turns in hilly areas.
				\item This project mainly revolves around configuring Ultrasound sensors , LED display , arduino , WiFi module and idiotware shield. Embedded C , Arduino IDE
				\item Won the Ist prize for this at Idiotware Hackathon. 
				\item \href{https://github.com/swekshajha12/Dodge_Hills}{Accident_Preventor}
				\item \textbf{Play Songs}. Desktop music player which can be synchronized from servers such as AWS , allowing users to play music in  their computer from those servers.  Python 
				\item \href{https://github.com/swekshajha12/compSpeakers}{Music_player}
				\item \textbf{Smart Factories}. It’s a composite system which can detect the moisture , temperature , light and harmful gases level . 
				\item It compares it with a threshold value and if the value becomes too low or high in comparison to threshold value then it buzzes an alarm to inform them.Embedded C , Arduino 
				\item \href{https://github.com/swekshajha12/IIOT}{Smart_factories}
				\item \textbf{Smart Vehicles}. This project tries to automate the process of maintenance of vehicles.
				\item Involved Configuration of MQ135 , LM35 sensors with node mcu and Thingspeak cloud.
				\item Selected For National Round of Tehno Champs 2016.
				\item \href{ https://github.com/swekshajha12/smart-tractors1}{Smart-vehicles}
				\item \textbf{Chatbot} Created a Simple chatbot using C++.
				\item Was among the top 5 out of 50 teams for this at Unocoin Cryptothon.
				\item \href{https://github.com/swekshajha12/chatbot}{Chatbot}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{GHCI 2017 Student Scholar:} Got selected for the student scholarship grannted to attend Grace Hopper Celebration Of India.
				\item \textbf{Ist Prize at Idiotware Hack 2017:} Awarded Ist prize for making an accident preventor at the hackathon.
				\item \textbf{10 cgpa in 10th}10 CGPA in class 10 AISSE Board exams.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Platforms}Linux and Windows
				\item \textbf{Libraries and Frameworks}Flask, Django, Arduino IDE
				\item \textbf{Databases}MySQL , Mongodb
				\item \textbf{Technologies} IOT , Web , AWS
				\item \textbf{Others} Git/Github
				\item \textbf{Competitive Coding Profile}\href{auth.geeksforgeeks.org/profile.php?user=techo&list=practice}{geekforgeeks}
				\item \textbf{Computer Languages}C,C++,JAVA,Python,HTML & CSS , Javascript , Shell , Embedded C
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
